### 2023-04-20 doc/definitions.tex
update definitions.tex

\begin{lemma}
\label{mixed_char_local_field.to_local_field}
\lean{mixed_char_local_field.to_local_field}
\uses{local_field, mixed_char_local_field}
A mixed characteristic local field is a local field.
\end{lemma}

\begin{lemma}
\label{eq_char_local_field.to_local_field}
\lean{eq_char_local_field.to_local_field}
\uses{local_field, eq_char_local_field}
An equal characteristic local field is a local field.
\end{lemma}

>>>>

\begin{lemma}
\label{mixed_char_local_field.local_field}
\lean{mixed_char_local_field.local_field}
\uses{local_field, mixed_char_local_field}
A mixed characteristic local field is a local field.
\end{lemma}

\begin{lemma}
\label{eq_char_local_field.local_field}
\lean{eq_char_local_field.local_field}
\uses{local_field, eq_char_local_field}
An equal characteristic local field is a local field.
\end{lemma}
